%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Martina Giron}{}

\position{Data Analyst}
\address{Makati City, Philippines}

\email{\href{mailto:msgiron@up.edu.ph}{\nolinkurl{msgiron@up.edu.ph}}}
\github{MartinaGiron}
\linkedin{martinagiron}
\twitter{martstats}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {}
    {Martina Giron~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{work-experience}{%
\section{Work Experience}\label{work-experience}}

\begin{cventries}
    \cventry{Technical Writer}{Towards Data Science}{August 2022 - Present}{}{\begin{cvitems}
\item Write tutorials on cleaning, visualizing, and analyzing data in R.
\item Document code in Github and create synthetic datasets to be used.
\end{cvitems}}
    \cventry{Data Intern}{Rappler}{July - August 2022}{}{\begin{cvitems}
\item Write data stories on relevant Philippine news and and issues.
\item Process data scraped from social media with R created interactive visualizations in Flourish.
\item Assist journalists in tagging online sources of misinformation
\end{cvitems}}
    \cventry{Research Volunteer}{PhilRights}{July - August 2022}{}{\begin{cvitems}
\item Organized records of human rights abuses in Microsoft Excel.
\item Identified areas with high incidence of human rights abuses and pinpointed common scenarios of extrajudicial killings.
\end{cvitems}}
\end{cventries}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{BS Statistics}{University of the Philippines-Diliman}{Quezon City, Philippines}{August 2019 - July 2023}{\begin{cvitems}
\item GWA: 1.30, DOST Merit Scholar, Dean's Commendation, and best in class for 5 units.
\item Consistent University Scholar (equivalent to President's List)
\item Studied courses on statistical inference, statistical quality control, scientific writing, and programming.
\end{cvitems}}
    \cventry{STEM Track}{Makati Science High School}{Makati City, Philippines}{June 2013 - April 2019}{\begin{cvitems}
\item Graduated with Honors
\end{cvitems}}
\end{cventries}

\hypertarget{data-analytics-projects}{%
\section{Data Analytics Projects}\label{data-analytics-projects}}

\hypertarget{visualizations-and-analyses}{%
\subsection{Visualizations and
Analyses}\label{visualizations-and-analyses}}

\begin{cvhonors}
    \cvhonor{}{\textbf{Forecasting with multiple seasonality}: Methods and techniques to multiple seasonal forecasting in R \newline \url{https://slides.mitchelloharawild.com/nhs2020/}}{}{2020}
    \cvhonor{}{\textbf{Probabilistic cross-temporal hierarchies}: Recent developments of temporal reconciliation in fable. \newline \url{https://slides.mitchelloharawild.com/isf2020/}}{}{2020}
    \cvhonor{}{\textbf{Flexible futures for fable functionality}: Gradual introduction to tidy forecasting with fable. Flexibility is demonstrated with combination modelling and package extensibilitiy. \newline \url{https://slides.mitchelloharawild.com/fable-tfeam/}}{}{2019}
    \cvhonor{}{\textbf{Flexible futures for fable functionality}: Reconciled forecasting of many time series with model combinations. \newline \url{https://slides.mitchelloharawild.com/isf2019/}}{}{2019}
    \cvhonor{}{\textbf{Tidy forecasting in R}: Discussion of recent developments to the fable framework. \newline \url{https://slides.mitchelloharawild.com/fable-tfeam/}}{}{2018}
    \cvhonor{}{\textbf{Forecasting multiple seasonality with state switching}: The FASSTER model with the fable framework. \newline \url{https://slides.mitchelloharawild.com/user2018}}{}{2018}
    \cvhonor{}{\textbf{Models for forecasting multiple seasonality}: An introduction to the FASSTER model. \newline \url{https://slides.mitchelloharawild.com/melburn17/}}{}{2017}
\end{cvhonors}

\hypertarget{articles-for-towards-data-science}{%
\subsection{Articles for Towards Data
Science}\label{articles-for-towards-data-science}}

\begin{cvhonors}
    \cvhonor{}{\textbf{Forecasting with multiple seasonality}: Methods and techniques to multiple seasonal forecasting in R \newline \url{https://slides.mitchelloharawild.com/nhs2020/}}{}{2020}
    \cvhonor{}{\textbf{Probabilistic cross-temporal hierarchies}: Recent developments of temporal reconciliation in fable. \newline \url{https://slides.mitchelloharawild.com/isf2020/}}{}{2020}
    \cvhonor{}{\textbf{Flexible futures for fable functionality}: Gradual introduction to tidy forecasting with fable. Flexibility is demonstrated with combination modelling and package extensibilitiy. \newline \url{https://slides.mitchelloharawild.com/fable-tfeam/}}{}{2019}
    \cvhonor{}{\textbf{Flexible futures for fable functionality}: Reconciled forecasting of many time series with model combinations. \newline \url{https://slides.mitchelloharawild.com/isf2019/}}{}{2019}
    \cvhonor{}{\textbf{Tidy forecasting in R}: Discussion of recent developments to the fable framework. \newline \url{https://slides.mitchelloharawild.com/fable-tfeam/}}{}{2018}
    \cvhonor{}{\textbf{Forecasting multiple seasonality with state switching}: The FASSTER model with the fable framework. \newline \url{https://slides.mitchelloharawild.com/user2018}}{}{2018}
    \cvhonor{}{\textbf{Models for forecasting multiple seasonality}: An introduction to the FASSTER model. \newline \url{https://slides.mitchelloharawild.com/melburn17/}}{}{2017}
\end{cvhonors}



\end{document}
